---
title: "README.Rmd"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r load-packages, message=FALSE}
library(tidyverse)
library(openintro)
library(ggplot2)
```

# Bechdel Test vs. Time Plots

Tip: RStudio menu bar -> Help -> Markdown Quick Reference for markdown formatting tips


### Establishing Dataframe

For SDS220 (Intro Probability/Stats) class, my final project group looked at data regarding the Bechdel test sourced from FiveThirtyEight. 

```{r}
movies_og <- read.csv("movies.csv")

# I noticed that the domgross and intgross variables are factors, so this changes them into quantitative variables so that we can apply mathematical operations. 
# Dataframe "movies_og" is the data from the csv file, but "movies" is what I'll be working with.
movies <- movies_og %>%  
  mutate(domgross = as.numeric(as.character(domgross)), intgross = as.numeric(as.character(intgross)))
```

## Some pretty plots!

These plots are from some data exploration I conducted for the project. They didn't make it into the final project, but I still enjoy them.

```{r}
fiveprops_by_year <- movies %>%
  group_by(year) %>%
  count(clean_test) %>%
mutate(fiveprops = n/sum(n))

p_fiveprops <- ggplot(fiveprops_by_year, aes(x=year, y=fiveprops, fill=clean_test)) + 
  geom_bar(position="stack", stat="identity")
p_fiveprops + labs(title="Proportions of Bechdel Test Statuses throughout Time", x="Year", y="Proportions", fill="Status")

p_fivenums <- ggplot(fiveprops_by_year, aes(x=year, y=n, fill=clean_test)) + 
  geom_bar(position="stack", stat="identity")
p_fivenums + labs(title="Bechdel Test Statuses throughout Time", x="Year", y="Number of Movies", fill="Status")

```
